Template for manuscript

### 2024-12-05 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.tex
Work on manuscript

\documentclass[fleqn,11pt,lineno]{manuscript}
%%\usepackage{setspace}
%%\doublespacing
\usepackage{soul}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R specifications
<<include = FALSE>>=
# knitr
library(knitr)
opts_chunk$set(fig.path = 'plots/p', 
               echo = FALSE, 
               results = 'hide',
               fig.height = 4.5,
               fig.align = "center",
               cache = TRUE)

# packages
require(xtable) # generating latex tables from datasets
require(data.table) # data wrangling
require(readxl) # importing excel tables

@
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

@@

<<laketable, results = "asis", echo=FALSE>>=
# Import lakemaster file
lakes <- read_excel("../../Organisation/GL_Lake_Master.xlsx")

# Extract relevant ponds
lakes <- lakes[c(18:23, 73:75, 78, 28, 83),]

# Extract columns
lakes <- lakes[,c("Lake", "Lat", "Long", "Areaha", "Altitude", "Depth")]

# Rename lakes
lakes$Lake <- c("B1P1", "B2P2", "B3P3", "B2P3", "B3P1", "B3P2", "B1P4", "B2P4",
                "B3P0", "ERL85", "ERL122", "ERL152")

# Rename
setnames(lakes, c("Lake", "Latitude (°N)", "Longitude (°E)", "Area (hectare)",
                  "Altitude (m)", "Maximum Depth (m)"))

# Create treatment variable
lakes$Treatment <- c("Fish","Fish","Fish","Fish","Fish","Fish",
                   "No Fish","No Fish","No Fish","No Fish","No Fish","No Fish")

# Reorder
lakes <- lakes[,c("Lake", "Treatment", "Latitude (°N)",
                  "Longitude (°E)", "Altitude (m)", "Area (hectare)",
                  "Maximum Depth (m)")]

# Make a latex table from dataset
lakes <- xtable(lakes, align = c("l","l","l","l","l","l","l","l"),
                digits = c(0,0,0,5,5,0,2,2),
                caption = "Lakes included in the experiment, along with treatment
                and general characteristics.", label = "tab:lakes")

# Print
print(lakes, include.rownames = FALSE, caption.placement = "top", booktabs = TRUE)
@

>>>>

\documentclass[fleqn,11pt,lineno]{manuscript}\usepackage[]{graphicx}\usepackage[]{xcolor}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlsng}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hldef}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
%%\usepackage{setspace}
%%\doublespacing
\usepackage{soul}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R specifications

\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Thu Dec  5 16:44:34 2024
\begin{table}[ht]
\centering
\caption{Lakes included in the experiment, along with treatment
                and general characteristics.} 
\label{tab:lakes}
\begin{tabular}{lllllll}
  \toprule
Lake & Treatment & Latitude (°N) & Longitude (°E) & Altitude (m) & Area (hectare) & Maximum Depth (m) \\ 
  \midrule
B1P1 & Fish & 61.15338 & -45.57081 & 272 & 0.21 & 4.00 \\ 
  B2P2 & Fish & 61.12299 & -45.55988 & 255 & 0.50 & 3.00 \\ 
  B3P3 & Fish & 61.13385 & -45.57556 & 258 & 0.30 & 5.00 \\ 
  B2P3 & Fish & 61.12275 & -45.55696 & 261 & 0.41 & 4.25 \\ 
  B3P1 & Fish & 61.13130 & -45.51195 & 180 & 0.40 & 2.00 \\ 
  B3P2 & Fish & 61.12788 & -45.51031 & 201 & 0.53 & 4.50 \\ 
  B1P4 & No Fish & 61.16552 & -45.56801 & 304 & 0.44 & 2.20 \\ 
  B2P4 & No Fish & 61.12192 & -45.55497 & 261 & 0.51 & 7.00 \\ 
  B3P0 & No Fish & 61.13210 & -45.51416 & 177 & 0.81 & 4.00 \\ 
  ERL85 & No Fish & 61.14171 & -45.59328 & 120 & 1.82 & 8.00 \\ 
  ERL122 & No Fish & 61.14182 & -45.53623 & 111 & 1.10 & 5.00 \\ 
  ERL152 & No Fish & 61.14646 & -45.59235 & 156 & 0.73 & 4.50 \\ 
   \bottomrule
\end{tabular}
\end{table}
